Real Time Genome Scan Using GPU

### 2019-07-22 paper.tex
adding julia gpu code sample

\articletype{inv} % article type
% {inv} Investigations
% {msr} Mutant Screen Reports
% {gs} Genomic Selection
% {goi} Genetics of Immunity 
% {gos} Genetics of Sex 
% {mp} Multiparental Populations
\usepackage{verbatim}
\usepackage{multirow}
%\usepackage{listings}
\newcommand{\code}{\texttt}

@@

The experiment setup is, to multiply two input matrices, A(mXn), and B(nXp), and produce an output matrix C(mXp)
The range of m, n and p is between 2\^4 and 2\^17 in log scale.
Due to the GPU hardware limitations, we can only compare the result when the size of input and output (I/O size) matrix total is less than 16 GB. 
The result is shown in Figure \ref{GPUCPUShape}. 
The X axis of Figure \ref{GPUCPUShape} is the dimensions of matrix whose I/O size is over 12 GB.
The Y axis is the speedup of GPU comparing to CPU in log scale.  
From this figure, the matrices whose shape are closer to a square matrix, get better speedup from GPU.

@@

\subsubsection{Julia language}
%Programming simplicity of interpreted languages with speed approaching compiled languages; GPU programming and linear algebra straightforward
In our experiment of matrix multiplication, Julia's speed is comparable to C/C++. 
However, the low learning curve, clean syntax, as well as support to GPU programming libraries such as CUDAnative and CuArrays affords much lower programming efforts compared to C/C++.
Compared to writting GPU functions in C/C++, writing in Julia is cleaner and easier, because it requires much less boiler plate code.
%TODO: Add reference to CUDAnative and CuArrays

\subsection{Information and Availability of Datasets}
Data from 79 BXD strains for 35556 transcripts from spleens were collected using the Affy Mouse Gene 1.0 ST array. Animals were generated by Drs. Lu, Williams, and colleagues. There were usually one male and one female per strain; strain averages were used as the trait of analysis. All animals were young adults (oldest 160 days). GN accession: GN283. Marker data was available on 7321 markers; genotype probabilities were calculated using R/qtl.

>>>>

\articletype{inv} % article type
% {inv} Investigations
% {msr} Mutant Screen Reports
% {gs} Genomic Selection
% {goi} Genetics of Immunity 
% {gos} Genetics of Sex 
% {mp} Multiparental Populations
\usepackage{verbatim}
\usepackage{multirow}
%\usepackage{listings}
\usepackage{minted}
\newcommand{\code}{\texttt}

@@

The experiment setup is, to multiply two input matrices, A(mXn), and B(nXp), and produce an output matrix C(mXp)
The range of m, n and p is between 2\textsuperscript{4} and 2\textsuperscript{17} in log scale.
Due to the GPU hardware limitations, we can only compare the result when the size of input and output (I/O size) matrix total is less than 16 GB. 
The result is shown in Figure \ref{GPUCPUShape}. 
The X axis of Figure \ref{GPUCPUShape} is the dimensions of matrix whose I/O size is over 12 GB.
This is because using GPU involves a lot of overhead. 
Such overhead can only be justified by processing large data sets. 
The Y axis is the speedup of GPU comparing to CPU in log scale.  
From this figure, the matrices whose shape are closer to a square matrix, get better speedup from GPU.

@@

\subsubsection{Julia language}
%Programming simplicity of interpreted languages with speed approaching compiled languages; GPU programming and linear algebra straightforward
In our experiment of matrix multiplication, Julia's speed is comparable to C/C++. 
However, the low learning curve, clean syntax, as well as support to GPU programming libraries such as CUDAnative and CuArrays affords much lower programming efforts compared to C/C++.
Compared to writting GPU functions in C/C++, writing in Julia is cleaner and easier, because it requires much less boiler plate code.

\inputminted{julia}{code/gpu.jl}
%TODO: Add reference to CUDAnative and CuArrays

\subsection{Information and Availability of Datasets}
Data from 79 BXD strains for 35556 transcripts from spleens were collected using the Affy Mouse Gene 1.0 ST array. Animals were generated by Drs. Lu, Williams, and colleagues. There were usually one male and one female per strain; strain averages were used as the trait of analysis. All animals were young adults (oldest 160 days). GN accession: GN283. Marker data was available on 7321 markers; genotype probabilities were calculated using R/qtl.
%TODO: add hippocampus data description.
